---
title: "build data"
output: html_document
date: "2024-06-26"
---

```{r setup, include=FALSE}
library(haven)
library(ltm)
library(tidyverse)
```


# load all wave 6 variables

```{r}
data = read_sav("/Users/andyouyang/Documents/research/Mali/data/afrobarometer_mli_r6_2015.sav")
```

```{r}
new_data <- bind_cols(
  RESP_NO = data$RESPNO,
  REGION = data$REGION,
  Q1 = data$Q1, # age
  
  # depr
  Q6A = data$Q8A,
  Q6B = data$Q8B,
  Q6C = data$Q8C,
  Q6D = data$Q8D,
  Q6E = data$Q8E,
  
  # response
  Q29B = data$Q28B, 
  
  Q37H = data$Q52I, # trust
  
  # corr
  Q38A = data$Q53A,
  Q38B = data$Q53B,
  Q38F = data$Q53F,
  
  Q84A = data$Q87, # ethnicity
  Q94 = data$Q97, # edu
  Q100 = data$Q101 # gender
)
```

```{r}
unique(new_data$REGION)
```


# load all violence data

We consider all under event type:

- Battles
- Violence against civilians
- Explosions/Remote violence

from 1997 to 2021 

we want to attach the total number of violent conflicts to each region in the original data


```{r}
violence = read.csv("/Users/andyouyang/Documents/research/tuki replication/Africa_1997-2024_Jun21.csv")
```


```{r}
# narrows down the year range, event type and country 

violence <- subset(violence, violence$year < 2015)
# unique(violence$event_date)
violence <- subset(violence, violence$event_type == "Battles" | 
                             violence$event_type == "Violence against civilians" | 
                             violence$event_type == "Explosions/Remote violence")
unique(violence$event_type)
violence <- subset(violence, violence$country == "Mali")
```

## matching the regions (9) to the violence dataset

matches with wikipedia: 

Bamako Capital District     509
Gao Region                  507
Kayes Region                501
Kidal Region                508
Koulikoro Region            502
Mopti Region                505
Ségou Region                504
Sikasso Region              503
Tombouctou Region           506

501	KAYES			
502	KOULIKORO			
503	SIKASSO			
504	SEGOU			
505	MOPTI			
506	TOMBOUCTOU			
507	GAO			   + Menaka
508	KIDAL			
509	BAMAKO

```{r}
# unique(violence$location)
# table(violence$location)
table(violence$admin1)
```

```{r}
new_data$vio_97_21[new_data$REGION == 509] <- 29 # bamako
new_data$vio_97_21[new_data$REGION == 508] <- 205 # kidal
new_data$vio_97_21[new_data$REGION == 507] <- 152 + 23 # Gao + Menaka
new_data$vio_97_21[new_data$REGION == 506] <- 122 # tombouctou
new_data$vio_97_21[new_data$REGION == 505] <- 47 # mopti
new_data$vio_97_21[new_data$REGION == 504] <- 17 # segou
new_data$vio_97_21[new_data$REGION == 503] <- 2 # sikasso 
new_data$vio_97_21[new_data$REGION == 502] <- 8 # koulikoro
new_data$vio_97_21[new_data$REGION == 501] <- 14 # kayes
```

```{r}
unique(new_data$vio_97_21)
```

# nighttime light

Nighttime light. This variable, which proxies economic development at the com-
munal level, measures the mean annual nighttime light in the region where the respon-
dents reside for the year 2020. Some studies have shown that nighttime light is a
good proxy for economic development. The nighttime light index ranges from 0
to 63, with higher values denoting a higher level of economic development and vice
versa. Since the raw dataset is gridded, I computed the relevant statistics for the
respective regions using QGIS software.

mean annual nighttime light in the region in 2020

501	KAYES			
502	KOULIKORO			
503	SIKASSO			
504	SEGOU			
505	MOPTI			
506	TOMBOUCTOU			
507	GAO		        (+ Menaka from gis data)
508	KIDAL			
509	BAMAKO

```{r}
new_data$night_2020mean[new_data$REGION == 509] <- 43.10139633120124 # bamako
new_data$night_2020mean[new_data$REGION == 508] <- 0.001223326080396386 # kidal
new_data$night_2020mean[new_data$REGION == 507] <- 0.004744900397549273 + 0
# gao and menaka
new_data$night_2020mean[new_data$REGION == 506] <- 0.0016399758969553942 # tombouctou
new_data$night_2020mean[new_data$REGION == 505] <- 0.028558963045724545 # mopti
new_data$night_2020mean[new_data$REGION == 504] <- 0.049822902317273925 # segou
new_data$night_2020mean[new_data$REGION == 503] <- 0.052385062984942624 # sikasso
new_data$night_2020mean[new_data$REGION == 502] <- 0.10708379773724264 # koulikoro
new_data$night_2020mean[new_data$REGION == 501] <- 0.046159147901255124 # kayes

unique(new_data$night_2020mean)
```

```{r}
new_data$year <- 2015
```

```{r}
write.csv(new_data,"~/Documents/research/clean_mali_data_round6.csv", row.names = FALSE)
```
